CTL mapping - The added value from segregating correlation

### 2012-02-09 inst/methodPaper/document.tex
Use EPS instead of PDF - PDF is not platform supported by latex

  \begin{figure*}[ht]
    \begin{center}
    \vspace{-0.2cm}
    \hspace{-1.3cm}
    \subfigure[CTL profiles]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_qtl.pdf}
      \label{subfiga}
    }
    \hspace{0.3cm}
    \subfigure[Traits x Traits interaction matrix]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_pxp.pdf}
      \label{subfigb}
    }
    \hspace{0.3cm}
    \subfigure[Reconstructed network]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_net.pdf}
      \label{subfigc}
    }
  \end{center}
  \begin{minipage}{7in}
  \label{newplots}
  \vspace{-0.7cm}
  \caption[Plots]{
  {\emph {\bf a}}: Example CTL + QTL profiles. Seen are the QTL profile on top of the CTL profile. 
  The first peak is a CTL, we don't observe a QTL for this location. The second peak is a QTL peek, with no underlying CTL. 
  {\emph {\bf b}}: Traits x Traits interaction matrix (TxT matrix). Information obtained using CTL mapping, 
  showing for each trait the significance of the difference in correlation to all other traits. This 
  matrix can be transformed into .sif file to generate a network image. 
  {\emph {\bf c}}:  Reconstructed network, this shows the same information as the TxT matrix only in a more accessible way, we visualized our 
  network using cytoscape, the width of the line is the maximum interaction evidence.
 }
\end{minipage}
\vspace{-0.5cm}
\end{figure*}

>>>>

  \begin{figure*}[ht]
    \begin{center}
    \vspace{-0.2cm}
    \hspace{-1.3cm}
    \subfigure[CTL profiles]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_qtl.eps}
      \label{subfiga}
    }
    \hspace{0.3cm}
    \subfigure[Traits x Traits interaction matrix]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_pxp.eps}
      \label{subfigb}
    }
    \hspace{0.3cm}
    \subfigure[Reconstructed network]{
      \includegraphics[keepaspectratio,scale=.3]{img/ctl_net.eps}
      \label{subfigc}
    }
  \end{center}
  \begin{minipage}{7in}
  \label{newplots}
  \vspace{-0.7cm}
  \caption[Plots]{
  {\emph {\bf a}}: Example CTL + QTL profiles. Seen are the QTL profile on top of the CTL profile. 
  The first peak is a CTL, we don't observe a QTL for this location. The second peak is a QTL peek, with no underlying CTL. 
  {\emph {\bf b}}: Traits x Traits interaction matrix (TxT matrix). Information obtained using CTL mapping, 
  showing for each trait the significance of the difference in correlation to all other traits. This 
  matrix can be transformed into .sif file to generate a network image. 
  {\emph {\bf c}}:  Reconstructed network, this shows the same information as the TxT matrix only in a more accessible way, we visualized our 
  network using cytoscape, the width of the line is the maximum interaction evidence.
 }
\end{minipage}
\vspace{-0.5cm}
\end{figure*}
